## statistical analysis

```{r eval=FALSE, include=FALSE}
#save the raw data -> raw database with all info and not only the tweet
# we want to keep the 5 variables
write.csv(tweet_trump, file = "TRUMP_raw.csv", row.names=FALSE)
write.csv(tweet_VP, file = "VP_raw.csv", row.names=FALSE)
write.csv(tweet_BIDEN, file = "BIDEN_raw.csv", row.names=FALSE)
write.csv(tweet_KAMALA, file = "KAMALA_raw.csv", row.names=FALSE)
############################################################################3
```

# Statistical analysis of tweets

In this part, we will simply analyze the statistics of each account analyzed. We don't use any developed text mining tools but only the collected data. 

## Daily tweets frequency
We analize all the tweets from the 2020-10-25 to 2020-11-05. We see that Donald Trump is tweeting more than the other candidates. We also notice a strong decrease in the number of tweets at the end of the campaign. Finally, we also notice that the Republican Vice President is discreet. 

```{r echo=FALSE, fig.height=3, fig.width=8, message=FALSE, warning=FALSE}
#open all the data
library(readr)
library(lubridate)
library(ggplot2)
library(kableExtra)
BIDEN_raw <- read_csv("raw_data/BIDEN_raw.csv")
KAMALA_raw <- read_csv("raw_data/KAMALA_raw.csv")

TRUMP_raw <- read_csv("raw_data/TRUMP_raw.csv")
VP_raw <- read_csv("raw_data/VP_raw.csv")

Biden_count <- BIDEN_raw %>% 
  mutate(date = date(created_at)) %>% 
  group_by(date) %>%
  summarise(biden_count = n()) %>% 
  filter(date >= "2020-10-25" & date <="2020-11-05")

Kamala_count <- KAMALA_raw %>% 
  mutate(date = date(created_at)) %>% 
  group_by(date) %>% 
  summarise(kamala_count = n())%>% 
  filter(date >= "2020-10-25" & date <="2020-11-05")

Trump_count <- TRUMP_raw %>% 
  mutate(date = date(created_at)) %>% 
  group_by(date) %>% 
  summarise(trump_count = n()) %>% 
  filter(date >= "2020-10-25" & date <= "2020-11-05")

VP_count <- VP_raw %>% 
  mutate(date = date(created_at)) %>% 
  group_by(date) %>% 
  summarise(vp_count = n()) %>% 
  filter(date >= "2020-10-25" & date <="2020-11-05")

merged <- left_join(Biden_count, Kamala_count)
merged <- left_join(merged, Trump_count)
merged <- left_join(merged, VP_count) 
#replace NA value
merged[is.na(merged)] <- 0
# create a plot
merged %>% ggplot(aes( x = date))+
  geom_line(aes(y = biden_count, color = "biden")) +
  geom_line(aes(y = kamala_count, color = "kamala")) +
  geom_line(aes(y = trump_count, color = "trump")) +
  geom_line(aes(y = vp_count, color = "pence")) +
  scale_y_continuous(breaks = seq(0 , 70, by = 5))+
  labs (x = "Year",
        y= "nb tweets",
        title = "number of daily tweets per candidate",
        subtitle = str_wrap("")) +
  guides(col=guide_legend("candidate"))



```

## others statistics

We can also analyze the average number of like or retweet. This shows the power of a candidate on social networks. 

Trump has more like, more retweet. Bidden also has a strong popularity on its tweets. This shows that twitter is a major instrument of politics in the USA. 

The candidate for vice president, Mrs. Harris also uses twitter a lot. For Mike Pence, on the other hand, he only retweets messages. He doesn't want to put himself forward. 

# IL FAUT ENCORE LE COMMENTER
```{r echo=FALSE}
#biden
BIDEN_raw %>% 
  mutate(date = date(created_at)) %>%
  filter(date >= "2020-10-25" & date <="2020-11-05") %>% 
  summarise(biden_like = mean(favorite_count),
            biden_RT = mean(retweet_count),
            biden_lengh = mean(display_text_width)) %>% 
 mutate_if(is.numeric, round) %>% 
 kable(caption = "Statistics for @JoeBiden", col.names = c("nb like", "nb retweet", "tweet length")) %>%
  kable_styling(
    bootstrap_options = "striped",
    full_width = F,
    position = "left"
  )

#kamala
KAMALA_raw %>% 
  mutate(date = date(created_at)) %>%
  filter(date >= "2020-10-25" & date <="2020-11-05") %>% 
  summarise(kamala_like = mean(favorite_count),
            kamala_RT = mean(retweet_count),
            kamala_lengh = mean(display_text_width)) %>% 
 mutate_if(is.numeric, round) %>% 
 kable(caption = "Statistics for @KamalaHarris", col.names = c("nb like", "nb retweet", "tweet length")) %>%
  kable_styling(
    bootstrap_options = "striped",
    full_width = F,
    position = "left"
  )

#trump
TRUMP_raw %>% 
  mutate(date = date(created_at)) %>%
  filter(date >= "2020-10-25" & date <="2020-11-05") %>% 
  summarise(trump_like = mean(favorite_count),
            trump_RT = mean(retweet_count),
            trump_lengh = mean(display_text_width)) %>% 
 mutate_if(is.numeric, round) %>% 
 kable(caption = "Statistics for @realDonaldTrump", col.names = c("nb like", "nb retweet", "tweet length")) %>%
  kable_styling(
    bootstrap_options = "striped",
    full_width = F,
    position = "left"
  )

#VP
VP_raw %>% 
  mutate(date = date(created_at)) %>%
  filter(date >= "2020-10-25" & date <="2020-11-05") %>% 
  summarise(vp_like = mean(favorite_count),
            vp_RT = mean(retweet_count),
            vp_lengh = mean(display_text_width)) %>% 
 mutate_if(is.numeric, round) %>% 
 kable(caption = "Statistics for @VP", col.names = c("nb like", "nb retweet", "tweet length")) %>%
  kable_styling(
    bootstrap_options = "striped",
    full_width = F,
    position = "left"
  )
```


```{r}
f <- file.path(here("data supervised_L/"), c("biden_after.csv","kamala_after.csv", "trump_after.csv", "vp_after.csv", "obama_after.csv", "aoc_after.csv"))
d <- lapply(f, read.csv)
str(d, give.attr = FALSE)

d <- Map(cbind, d, name = c("Biden", "Kamala", "Trump", "VP", "obama", "aoc"))

tweet_all <- rbind(d[[1]], d[[2]], d[[3]], d[[4]],d[[5]],d[[6]])


# 2weeks befores and 2 weeks after
tweet_all %>%  select(-name) %>% 
  mutate(date_created = date(created_at)) %>% 
  filter(date_created >= "2020-10-20" & date_created <= "2020-11-17") %>%
  select(screen_name, favorite_count, retweet_count, display_text_width) %>% 
  group_by(screen_name) %>% 
  summarise(mean_favorite = mean(favorite_count),
            mean_retweet = mean(retweet_count),
            mean_text_width = mean(display_text_width)) %>% 
  arrange(desc(mean_favorite)) %>% 
  mutate(mean_retweet = round(mean_retweet, 0),
         mean_favorite = round(mean_favorite, 0),
         mean_text_width = round(mean_text_width, 0)) %>% 
 kable(caption = "Statistics for @VP", col.names = c("name","avg_like", "avg_retweet", "avg_tweet_length")) %>%
  kable_styling(
    bootstrap_options = "striped",
    full_width = F,
    position = "left"
  )
  
```






