---
title: "Text Mining"
author: "Vuignier, Cédric - Lovey, Gaëtan - Vo-Ngoc Michael"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  rmdformats::readthedown:
    code_folding: hide
    toc_depth: 4
---

```{r include=FALSE}
library(graphics)
library(textclean)
library(stringr)
library(purrr)
library(rlang)
library(dplyr)
library(tibble)
library(syuzhet)
library(NLP)
library(tm)
library(rtweet)
library(reactable)
library(httpuv)
library(here)
library(readtext)
library(foreign)
library(quanteda)
library(readr)
library(lubridate)
library(ggplot2)
library(kableExtra)
library(tidyverse)
library(tidytext)
library(textdata)
library(wordcloud)
library(quanteda.textmodels)
library(caret)
library(ranger)
library(lexicon)
library(qdapRegex)
library(text2vec)

```

### literature importante

- clean the tweet : https://towardsdatascience.com/text-mining-with-r-gathering-and-cleaning-data-8f8b0d65e67c 
- set your twitter API : https://www.infoworld.com/article/3515712/how-to-search-twitter-with-rtweet-and-r.html  
- scrapp by hashtag or region or user : https://cran.r-project.org/web/packages/rtweet/vignettes/intro.html 

### connect to API twitter

#only run this now if the point 2 is not done yet. 
twitter log-in (need to register the account in the pop-up windows)
name : textmining13
mdp : textmining2020

```{r message=FALSE, warning=FALSE, eval=FALSE}
library(rtweet)
get_token()

```

 no need to run the following code if you have already done this part. 
 follow the instruction to link your twitter app with your R CONSOL. Do it only once. 
```{r message=FALSE, warning=FALSE, eval=FALSE}
## load rtweet
library(rtweet)

## store api keys (these are fake example values; replace with your own keys)
api_key <- "cFRZi4lsJGD4DxrtLT24za5UH"
api_secret_key <- "iHBlU1fA5WdQ17N3udi8FWg8TlwugXb8e6c34MNRGmKXNJFIQY"

## authenticate via web browser
token <- create_token(
  app = "TextMiningHEC",
  consumer_key = api_key,
  consumer_secret = api_secret_key)

#verify it

#token
```

```{r child = 'Part_I_scrapping.Rmd'}
```

```{r child = 'Part_II_stat_analysis.Rmd'}
```

```{r child = 'Part_III_analysis.Rmd'}
```





