## Tweet scrcapping

### Get the tweets
We collect the 3000 last tweets from TRUMP, JOE BIDEN, KAMALA HARRIS, MIKE PENCE. the DF has 90 variable. It's way too much. 

Twitter sets a limit of 3200 tweets per request. So we have to do the same operation for each account (@).
```{r message=FALSE, warning=FALSE, eval=FALSE}
#split the scrapping into two part to avoid the limit 
#########REPUCLICAN#############################
#we see that MIKE PENCE the vice president of donald trump doesn't tweet. He only retweet. so we scrap manually the Retweet for him
tweet_trump <- get_timelines("realDonaldTrump", n = 3000, 
            include_rts = FALSE)

#get the hastag trump
tweet_trump_hashtag <- search_tweets(
  "#Trump", n = 2000, include_rts = FALSE
)

#vice president tweet
tweet_VP <- get_timelines("VP", n = 3000, 
            include_rts = TRUE)

#########DEMOCRATE#############################

tweet_BIDEN <- get_timelines("JoeBiden", n = 3000, 
            include_rts = FALSE)

#get the hastage biden
tweet_biden_hashtag <- search_tweets(
  "#Biden", n = 2000, include_rts = FALSE
)

#the vice president selected by biden if he is elected 
tweet_KAMALA <- get_timelines("KamalaHarris", n = 3000, 
            include_rts = FALSE)
```

### explain the data

we will only keep the variable *text*, *created at*, *retweet_count*, *favorite_count* and *display_text_width* in order to do some basics statistics analysis. 
```{r eval=FALSE, include=FALSE}
#TRUMP
tweet_trump <- tweet_trump %>% 
  select(text, created_at, retweet_count, favorite_count,display_text_width)
#VP
tweet_VP <- tweet_VP %>% 
  select(text, created_at, retweet_count, favorite_count,display_text_width)
#BIDEN
tweet_BIDEN <- tweet_BIDEN %>% 
  select(text, created_at, retweet_count, favorite_count,display_text_width)
#KAMALA
tweet_KAMALA <- tweet_KAMALA %>% 
  select(text, created_at, retweet_count, favorite_count,display_text_width)

##### hashtag part (trump and biden)
tweet_trump_hashtag <- tweet_trump_hashtag %>% 
  select(text, created_at, retweet_count, favorite_count,display_text_width)

tweet_biden_hashtag <- tweet_biden_hashtag %>% 
  select(text, created_at, retweet_count, favorite_count,display_text_width)
```

Below is an example with ten random tweets from Joe Biden. 
```{r echo=FALSE, message=FALSE, warning=FALSE}
#generate a shiny graph (trump)

table_B <- read_csv("raw_data/table_Biden_example.csv")

table_B$text <- gsub("@\\w+", "", table_B$text)
table_B$text <- gsub("https?://.+", "", table_B$text)
table_B$text <- gsub("\\d+\\w*\\d*", "", table_B$text)
table_B$text <- gsub("#\\w+", "", table_B$text)
table_B$text <- gsub("[^\x01-\x7F]", "", table_B$text)
table_B$text <- gsub("[[:punct:]]", " ", table_B$text)

reactable(table_B, 
          filterable = TRUE, searchable = TRUE, bordered = TRUE, 
          striped = TRUE, highlight = TRUE,
          defaultPageSize = 25, showPageSizeOptions = TRUE, 
          showSortable = TRUE, pageSizeOptions = c(25, 50, 75, 100, 200), defaultSortOrder = "desc",
            columns = list(
            created_at = colDef(defaultSortOrder = "asc"),
            text = colDef(html = TRUE, minWidth = 190, resizable = TRUE),
            favorite_count = colDef(filterable = FALSE),
            retweet_count = colDef(filterable =  FALSE),
            display_text_width = colDef(filterable =  FALSE)
          )
) 
```

### clean the data 
diffult to read so we have to improve the data set. We have to remove a lot of useless information like:
- URL
- User
- some emoji or special character

only keep the text and transform it 
```{r eval=FALSE, include=FALSE}
#TRUMP#############################################
#KEEP ONLY THE TWEET
TRUMP <- tweet_trump %>% 
  select(text)
#not so readable, so we have to modify a bit our data structure.
head(TRUMP)

# Get the text column
TRUMP <- TRUMP$text
# Set the text to lowercase
TRUMP <- tolower(TRUMP)
# Remove mentions, urls, emojis, numbers, punctuations, etc.
TRUMP <- gsub("@\\w+", "", TRUMP)
TRUMP <- gsub("https?://.+", "", TRUMP)
TRUMP <- gsub("\\d+\\w*\\d*", "", TRUMP)
TRUMP <- gsub("#\\w+", "", TRUMP)
TRUMP <- gsub("[^\x01-\x7F]", "", TRUMP)
TRUMP <- gsub("[[:punct:]]", " ", TRUMP)
# Remove spaces and newlines
TRUMP <- gsub("\n", " ", TRUMP)
TRUMP <- gsub("^\\s+", "", TRUMP)
TRUMP <- gsub("\\s+$", "", TRUMP)
TRUMP <- gsub("[ |\t]+", " ", TRUMP)
#rename variable
TRUMP <- as_tibble(TRUMP)
# drop empty values
TRUMP <- TRUMP[!(is.na(TRUMP$value) | TRUMP$value==""), ]

#VP#############################################
#BIDEN
#KEEP ONLY THE TWEET
VP <- tweet_VP %>% 
  select(text)
#not so readable, so we have to modify a bit our data structure.
head(VP)

# Get the text column
VP <- VP$text
# Set the text to lowercase
VP <- tolower(VP)
# Remove mentions, urls, emojis, numbers, punctuations, etc.
VP <- gsub("@\\w+", "", VP)
VP <- gsub("https?://.+", "", VP)
VP <- gsub("\\d+\\w*\\d*", "", VP)
VP <- gsub("#\\w+", "", VP)
VP <- gsub("[^\x01-\x7F]", "", VP)
VP <- gsub("[[:punct:]]", " ", VP)
# Remove spaces and newlines
VP <- gsub("\n", " ", VP)
VP <- gsub("^\\s+", "", VP)
VP <- gsub("\\s+$", "", VP)
VP <- gsub("[ |\t]+", " ", VP)
#rename variable
VP <- as_tibble(VP)
# drop empty values
VP <- VP[!(is.na(VP$value) | VP$value==""), ]

#BIDEN#############################################
#KEEP ONLY THE TWEET
BIDEN <- tweet_BIDEN %>% 
  select(text)
#not so readable, so we have to modify a bit our data structure.
head(BIDEN)

# Get the text column
BIDEN <- BIDEN$text
# Set the text to lowercase
BIDEN <- tolower(BIDEN)
# Remove mentions, urls, emojis, numbers, punctuations, etc.
BIDEN <- gsub("@\\w+", "", BIDEN)
BIDEN <- gsub("https?://.+", "", BIDEN)
BIDEN <- gsub("\\d+\\w*\\d*", "", BIDEN)
BIDEN <- gsub("#\\w+", "", BIDEN)
BIDEN <- gsub("[^\x01-\x7F]", "", BIDEN)
BIDEN <- gsub("[[:punct:]]", " ", BIDEN)
# Remove spaces and newlines
BIDEN <- gsub("\n", " ", BIDEN)
BIDEN <- gsub("^\\s+", "", BIDEN)
BIDEN <- gsub("\\s+$", "", BIDEN)
BIDEN <- gsub("[ |\t]+", " ", BIDEN)
#rename variable
BIDEN <- as_tibble(BIDEN)
# drop empty values
BIDEN <- BIDEN[!(is.na(BIDEN$value) | BIDEN$value==""), ]

#KAMALA#############################################
#KEEP ONLY THE TWEET
KAMALA <- tweet_KAMALA %>% 
  select(text)
#not so readable, so we have to modify a bit our data structure.
head(KAMALA)

# Get the text column
KAMALA <- KAMALA$text
# Set the text to lowercase
KAMALA <- tolower(KAMALA)
# Remove mentions, urls, emojis, numbers, punctuations, etc.
KAMALA <- gsub("@\\w+", "", KAMALA)
KAMALA <- gsub("https?://.+", "", KAMALA)
KAMALA <- gsub("\\d+\\w*\\d*", "", KAMALA)
KAMALA <- gsub("#\\w+", "", KAMALA)
KAMALA <- gsub("[^\x01-\x7F]", "", KAMALA)
KAMALA <- gsub("[[:punct:]]", " ", KAMALA)
# Remove spaces and newlines
KAMALA <- gsub("\n", " ", KAMALA)
KAMALA <- gsub("^\\s+", "", KAMALA)
KAMALA <- gsub("\\s+$", "", KAMALA)
KAMALA <- gsub("[ |\t]+", " ", KAMALA)
#rename variable
KAMALA <- as_tibble(KAMALA)
# drop empty values
KAMALA <- KAMALA[!(is.na(KAMALA$value) | KAMALA$value==""), ]

#########################hashtag cleaning###############################
#trump
#KEEP ONLY THE TWEET
tweet_trump_hashtag <- tweet_trump_hashtag %>% 
  select(text)
#not so readable, so we have to modify a bit our data structure.
head(tweet_trump_hashtag)

# Get the text column
tweet_trump_hashtag <- tweet_trump_hashtag$text
# Set the text to lowercase
tweet_trump_hashtag <- tolower(tweet_trump_hashtag)
# Remove mentions, urls, emojis, numbers, punctuations, etc.
tweet_trump_hashtag <- gsub("@\\w+", "", tweet_trump_hashtag)
tweet_trump_hashtag <- gsub("https?://.+", "", tweet_trump_hashtag)
tweet_trump_hashtag <- gsub("\\d+\\w*\\d*", "", tweet_trump_hashtag)
tweet_trump_hashtag <- gsub("#\\w+", "", tweet_trump_hashtag)
tweet_trump_hashtag <- gsub("[^\x01-\x7F]", "", tweet_trump_hashtag)
tweet_trump_hashtag <- gsub("[[:punct:]]", " ", tweet_trump_hashtag)
# Remove spaces and newlines
tweet_trump_hashtag <- gsub("\n", " ", tweet_trump_hashtag)
tweet_trump_hashtag <- gsub("^\\s+", "", tweet_trump_hashtag)
tweet_trump_hashtag <- gsub("\\s+$", "", tweet_trump_hashtag)
tweet_trump_hashtag <- gsub("[ |\t]+", " ", tweet_trump_hashtag)
#rename variable
tweet_trump_hashtag <- as_tibble(tweet_trump_hashtag)
# drop empty values
tweet_trump_hashtag <- tweet_trump_hashtag[!(is.na(tweet_trump_hashtag$value) | tweet_trump_hashtag$value==""), ]


#biden
#KEEP ONLY THE TWEET
tweet_biden_hashtag <- tweet_biden_hashtag %>% 
  select(text)
#not so readable, so we have to modify a bit our data structure.
head(tweet_biden_hashtag)

# Get the text column
tweet_biden_hashtag <- tweet_biden_hashtag$text
# Set the text to lowercase
tweet_biden_hashtag <- tolower(tweet_biden_hashtag)
# Remove mentions, urls, emojis, numbers, punctuations, etc.
tweet_biden_hashtag <- gsub("@\\w+", "", tweet_biden_hashtag)
tweet_biden_hashtag <- gsub("https?://.+", "", tweet_biden_hashtag)
tweet_biden_hashtag <- gsub("\\d+\\w*\\d*", "", tweet_biden_hashtag)
tweet_biden_hashtag <- gsub("#\\w+", "", tweet_biden_hashtag)
tweet_biden_hashtag <- gsub("[^\x01-\x7F]", "", tweet_biden_hashtag)
tweet_biden_hashtag <- gsub("[[:punct:]]", " ", tweet_biden_hashtag)
# Remove spaces and newlines
tweet_biden_hashtag <- gsub("\n", " ", tweet_biden_hashtag)
tweet_biden_hashtag <- gsub("^\\s+", "", tweet_biden_hashtag)
tweet_biden_hashtag <- gsub("\\s+$", "", tweet_biden_hashtag)
tweet_biden_hashtag <- gsub("[ |\t]+", " ", tweet_biden_hashtag)
#rename variable
tweet_biden_hashtag <- as_tibble(tweet_biden_hashtag)
# drop empty values
tweet_biden_hashtag <- tweet_biden_hashtag[!(is.na(tweet_biden_hashtag$value) | tweet_biden_hashtag$value==""), ]
```

#FINALY WE SAVE OUR DATAFRAME
```{r eval=FALSE, include=FALSE}
write.csv(TRUMP, file = "TRUMP_all_tweet.csv", row.names=FALSE)
write.csv(VP, file = "VP_all_tweet.csv", row.names=FALSE)
write.csv(BIDEN, file = "BIDEN_all_tweet.csv", row.names=FALSE)
write.csv(KAMALA, file = "KAMALA_all_tweet.csv", row.names=FALSE)

#hashtag csv
write.csv(tweet_trump_hashtag, file = "hashtag_trump.csv", row.names=FALSE)
write.csv(tweet_biden_hashtag, file = "hashtag_biden.csv", row.names=FALSE)
```